Accurate relative location using coda waves of a poorly recorded cluster of earthquakes near Kalannie, Western Australia

### 2012-07-31 paper3/paper3.tex
fiddling with the Kalannie Map
now have it working from local copies of figures.aux

%%% End the article here:
\clearpage
\begin{figure}
\begin{tabular}{ll}
(a) & (b) \\
\multirow{15}{*}{\includegraphics[width = 16pc]{../../thesis_version2/diags/eq_location_simple/KalannieMap/KalannieMap1.eps}} &
\multirow{15}{*}{\includegraphics[width = 20pc]{diags/waves_and_CWIest.eps}} \\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\end{tabular}
\caption{(a) Map of the South West Seismic Zone (SWSZ) illustrating the location of the Kalannie earthquake cluster,
the \cite{dr_Dawson08a} composite focal mechanism for the Kalannie events,
large historical events (focal mechanisms), observed seismicity between 1998 to 2007 (circles) and
Quaternary fault scarps (black lines) identified by \citet{dr_Clark09a}. The three available recording stations
MORW (162\,km), BLDU (67\,km) and KLBR (169\,km) are depicted with red triangles. Figure courtesy of
\citet{dr_Dawson08a} with minor modifications. (b) Example waveforms and CWI separation estimates
for the Kalannie events. The top row illustrates waveforms at station MORW for Event 1 normalised to maximum
amplitude and filtered between 1 and 2\,Hz for the three channels N,Z,E. Relative P, S and surface wave arrivals are also
indicated at 0, 19 and 27\,s, respectively. Middle row demonstrates similarity of first arrivals at station MORW for Events 1 and 2 in
the three channels. The bottom row shows the CWI separation estimates at MORW
as a function of sliding time window with width 5\,s for event pair 1 and 2. The three traces
represent different channels and the vertical black lines
enclose the region between $t=$5\,s and $t_{surf}$ that we consider for the remaining analysis.}
\label{fig:-Kalannie-map}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_simple/Kalannie_figs/Kalannie_Posteriors_timeclip_1to2Hz_tw5.eps}
\caption{Posterior functions $P_{ij}(\widetilde{\delta}_{t}|\widetilde{\delta}_{CWIN})$ for the Kalannie
event pairs $i$ and $j$. A
second $x$-axis is shown in separation units of meters for convenience.}
\label{fig:Kalannie-CWI-Posteriors}
\end{figure}

\begin{figure}
\begin{tabular}{ll}
(a) & (b) \\
\multirow{3}{*}{\noindent\includegraphics[width = 25pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie-CWI-NAB-1Dmarginals-withareas.eps}} & \multirow{2}{*}{\includegraphics[width = 10pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_covariance.eps}}\\
&  \\
 & \\
 &
 \\
\\
\\
\\
\\
& (c) \\
&  \multirow{2}{*}{\includegraphics[width = 10pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_correlation.eps}}\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\end{tabular}
\caption{(a) One dimensional marginals for each of the six unknown Kalannie earthquake coordinates.
Labels $\hat{x}$, $\hat{y}$ and $\hat{z}$ refer to a local coordinate system with
origin corresponding to the event 1 location. Subscripts indicate the event number. Missing
parameters $\hat{y}_2$, $\hat{z}_2$ and $\hat{z}_3$ are set to 0 to remove rotational non-uniqueness without
loss of generality. Grey shaded regions illustrate the probability of each coordinate
being within 500\,m of the origin. The relative size of the shaded area
indicates that all event coordinates are likely within 500\,m of event 1
(see table \ref{tab:Kalannie-InversionRes} for actual areas). (b) Covariance and (c) correlation matrices
for the Kalannie earthquake location coordinates.
Different colours in the covariance matrix suggest different levels of resolvability between
coordinates. The off-diagonal structure of the correlation matrix indicates
a low level of trade-off between different coordinates.}
\label{fig:Kalannie-CWI-NAB-1Dmarginals}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=20pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_marginals2Dcont_param2_3.eps} \\
\caption{Marginal $P(\mathbf{e}_3) = P(\hat{x}_3,\hat{y}_3)$  for the location of event 3 normalised to unit volume.
We observe a clear maximum
near ($\hat{x}_3=290$\,m, $\hat{y}_3=300$\,m) and a local minimum near the origin. The black lines
enclose the 68\% confidence region. This figure suggests that events 3 and 1 (at origin) are close to one another but
not co-located and is consistent with the inversion results from the optimiser (magenta circle) and
MCMC (green circle).}
\label{fig:Kalannie-2Dmarginals_param23}
\end{figure}

>>>>

%%% End the article here:
\clearpage
\begin{figure}
\begin{tabular}{ll}
(a) & (b) \\
\multirow{15}{*}{\includegraphics[width =
16pc]{./diags/KalannieMap/KalannieMap1.eps}} &
\multirow{15}{*}{\includegraphics[width = 20pc]{diags/waves_and_CWIest.eps}} \\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\end{tabular}
\caption{(a) Map of the South West Seismic Zone (SWSZ) illustrating the location of the Kalannie earthquake cluster,
the \cite{dr_Dawson08a} composite focal mechanism for the Kalannie events,
large historical events (focal mechanisms), observed seismicity between 1998 to 2007 (circles) and
Quaternary fault scarps (black lines) identified by \citet{dr_Clark09a}. The three available recording stations
MORW (162\,km), BLDU (67\,km) and KLBR (169\,km) are depicted with red triangles. Figure courtesy of
\citet{dr_Dawson08a} with minor modifications. (b) Example waveforms and CWI separation estimates
for the Kalannie events. The top row illustrates waveforms at station MORW for Event 1 normalised to maximum
amplitude and filtered between 1 and 2\,Hz for the three channels N,Z,E. Relative P, S and surface wave arrivals are also
indicated at 0, 19 and 27\,s, respectively. Middle row demonstrates similarity of first arrivals at station MORW for Events 1 and 2 in
the three channels. The bottom row shows the CWI separation estimates at MORW
as a function of sliding time window with width 5\,s for event pair 1 and 2. The three traces
represent different channels and the vertical black lines
enclose the region between $t=$5\,s and $t_{surf}$ that we consider for the remaining analysis.}
\label{fig:-Kalannie-map}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=20pc]{./diags/CopiedFromThesis/Kalannie_Posteriors_timeclip_1to2Hz_tw5.eps}
\caption{Posterior functions
$P_{ij}(\widetilde{\delta}_{t}|\widetilde{\delta}_{CWIN})$ for the
Kalannie event pairs $i$ and $j$. A second $x$-axis is shown in
separation units of meters for convenience.}
\label{fig:Kalannie-CWI-Posteriors}
\end{figure}

\begin{figure}
\begin{tabular}{ll}
(a) & (b) \\
\multirow{3}{*}{\noindent\includegraphics[width=25pc]{./diags/CopiedFromThesis/Kalannie-CWI-NAB-1Dmarginals-withareas.eps}}
 %{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie-CWI-NAB-1Dmarginals-withareas.eps}}
& \multirow{2}{*}{\includegraphics[width=10pc]{./diags/CopiedFromThesis/Kalannie_covariance.eps}}\\
%{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_covariance.eps}}\\
&  \\
 & \\
 &
 \\
\\
\\
\\
\\
& (c) \\
&
\multirow{2}{*}{\includegraphics[width=10pc]{./diags/CopiedFromThesis/Kalannie_correlation.eps}}
%{\includegraphics[width = 10pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_correlation.eps}}\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\end{tabular}
\caption{(a) One dimensional marginals for each of the six unknown Kalannie earthquake coordinates.
Labels $\hat{x}$, $\hat{y}$ and $\hat{z}$ refer to a local coordinate system with
origin corresponding to the event 1 location. Subscripts indicate the event number. Missing
parameters $\hat{y}_2$, $\hat{z}_2$ and $\hat{z}_3$ are set to 0 to remove rotational non-uniqueness without
loss of generality. Grey shaded regions illustrate the probability of each coordinate
being within 500\,m of the origin. The relative size of the shaded area
indicates that all event coordinates are likely within 500\,m of event 1
(see table \ref{tab:Kalannie-InversionRes} for actual areas). (b) Covariance and (c) correlation matrices
for the Kalannie earthquake location coordinates.
Different colours in the covariance matrix suggest different levels of resolvability between
coordinates. The off-diagonal structure of the correlation matrix indicates
a low level of trade-off between different coordinates.}
\label{fig:Kalannie-CWI-NAB-1Dmarginals}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=20pc]{./diags/CopiedFromThesis/Kalannie_marginals2Dcont_param2_3.eps}
%{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_marginals2Dcont_param2_3.eps} \\
\caption{Marginal $P(\mathbf{e}_3) = P(\hat{x}_3,\hat{y}_3)$  for the location of event 3 normalised to unit volume.
We observe a clear maximum
near ($\hat{x}_3=290$\,m, $\hat{y}_3=300$\,m) and a local minimum near the origin. The black lines
enclose the 68\% confidence region. This figure suggests that events 3 and 1 (at origin) are close to one another but
not co-located and is consistent with the inversion results from the optimiser (magenta circle) and
MCMC (green circle).}
\label{fig:Kalannie-2Dmarginals_param23}
\end{figure}
